---
title: "process-dye-screen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{process-dye-screen}
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dsfworld)
```

Minimal version of dye screen processing in an R notebook!
For non-dye screen processing, you can try following the worflow in the previous R notebook I sent!

I try to follow tidyverse workflows and conventions as much as possible.
The tidyverse is a suite of packages designed to work together to solve common data science problems in coding.
Tidyverse documentation: https://www.tidyverse.org/
Tidyverse coding style guide: https://style.tidyverse.org/

I sent you the folder containing the actual current version of the package (which is still in development). 
I'd recommend just using source(<R script name.R>) to read in the individual functions, instead of trying to locally install the package. But do what you think is best!
FMI on package structure, see the book I followed to build the package
https://r-pkgs.org/index.html

Good luck!

I tried to make this notebook easy to re-use. 
Where I think you'll have to make changes with each screen, i added #__USER_UPDATES__

Read in libraries
```{r}
# these three packaged are used in workflow in this notebook
library(tidyverse) # actually a suite of packages
library(fs) # nice filesystem management, used by/with the tidyverse
library(glue) # nice alternative to paste functions, used to create screen and save names, and used by/with the tidyverse

# this has all of the actual code for processing dye screens
library(dsfworld) # you'll likely have to replace this with a series of "source()" calls with the R script names containing the functions. 
```

Assign some information about your screen, so it's easy to propagate through the following code
```{r}
# names / details of screen
set_protein_name <- "SP115_NHR23LBD" #__USER_UPDATES__
set_screen_num <- "Exp1236" #__USER_UPDATES__
set_buffer_used <- "Buffer_P1" #__USER_UPDATES__

# i like to divide outputs in to different folders. 
# create those folders here
# choose the folder names
plot_folder <- "plots" # save the output plots
assignments_folder <- "assignments" # save the manual hit assigments df and csv
int_folder <- "int"  # save the tidied raw data
# i already have"layout" and "raw" folders in the working directory where this notebook is saved

# create the directories (or you can do it manually)
# using the fs library, whih is good and safe. 
fs::dir_create(plot_folder) 
fs::dir_create(assignments_folder) 
fs::dir_create(int_folder)
```

Assign directories to files that need to be read
```{r}
# protein_layout_path <- "layout/layout_861_rank_ordered_dye_daughters.xlsx" #__USER_UPDATES__# in this case, the same for protein and buffer
# buffer_layout_path <- "layout/layout_861_rank_ordered_dye_daughters.xlsx" #__USER_UPDATES__# in this case, the same for protein and buffer
# 
# raw_protein_path <- "raw/Exp1152--20210519_SP115_NHR23LBD_dye_screen_861.csv" #__USER_UPDATES__
# raw_buffer_path <- "raw/Exp0724--20191017_OGlcNacTransferase_SP029_buffer_dye_screen_715.csv" #__USER_UPDATES__
# 
# # protein and buffer data don't need the have the same layout. 
# # if the layouts are different, read both in, and pass both to tidied_dye_screen(). See below. 
```

Step 1: Read in the raw screens and layouts
```{r}
# ##### unless you want to 
# protein_layout <- # check out documentation--this layout reader is more flexible than the one on the websites
#   read_plate_layout(protein_layout_path)
# 
# buffer_layout <- # check out documentation--this layout reader is more flexible than the one on the websites
#   read_plate_layout(buffer_layout_path)
# 
# raw_protein <- # path to a raw qTower csv
#   read_qtower(raw_protein_path)
# 
# raw_buffer <- # path to a raw qTower csv
#   read_qtower(raw_buffer_path)
# 
# tidied_screen <- # creates / enforces expectations on the data structure of dye screens
#   tidy_dye_screen(.raw_data = raw_protein,
#                   .raw_layout = protein_layout,
#                   .buffer_data = raw_buffer,
#                   .buffer_layout = buffer_layout,
#                   .protein_name = set_protein_name,
#                   .exp_num = set_screen_num,
#                   .buffer_used = set_buffer_used,
#                   
#                   ####  these arguments are passed to label_dye_screen via() ...
#                   #  defaults column names correspond to the echowritr package outputs. 
#                   # see documentation for label_dye_screen() FMI
#                   .dye_col = "compound", #__USER_UPDATES__
#                   .dye_conc_col = "concentration" #__USER_UPDATES__
#                   )
```

Step 2: save the tidied screen
```{r}
# write_rds(x = tidied_screen,
#           file = glue::glue("{int_folder}/{set_screen_num}--{glue::glue_collapse(gsub(Sys.Date(), pattern = '-', replacement = ''))}_{set_protein_name}_df_all.rds"))
```

Make the standard dye screen plot
```{r}
# full_screen_p <- # takes a minute
#   save_dye_screen_figs(tidied_screen, 
#                        plot_type = "full_screen",
#                        
#                        # passed to saved_stacked_screen() via ...
#                        .save_path = plot_folder)
```

Call hits
This is meant to work with the manual hit selections csv that is created by clicking on the website.
In non-interactive versions, for nowm=, just write them as vectors and run this code

If you already have this manual assignments csv saved and read it in via 
hit_df <- read_csv(<path to your csv>)
You can then bypass the creation and saving to hit_df (next two chunks)
```{r}
# ####### USER UPDATES THESE ASSIGNMENTS WITH EACH SCREEN
# ## ---- look at the raw data plot to make decisions
# hit_dyes <- # called just a couple, to illustrate example
#   c("A002" ,"A014", "TW408") #__USER_UPDATES__
# 
# sensitive_dyes <- # called just a couple, to illustrate example
#   c( "A003", "L098", "L098") #__USER_UPDATES__
```

Create the assignment df from the user-defined hits
```{r}
# hit_df <-
#   # initially, assign every dye "none" 
#   tibble(dye = unique(tidied_screen$dye),
#          assignment = "none") %>%
#   
#   mutate(assignment = if_else(dye %in% hit_dyes, # amend if "hit"
#                               true = "hit",
#                               false = assignment),
#          assignment = if_else(dye %in% sensitive_dyes, # amend if "sensitive
#                               true = "sensitive",
#                               false = assignment))
# 
# hit_df # see requirements for hit_df in the documentation ofr save_dye_screen_figs()
# 
# assignment_df_name <- glue::glue("{set_screen_num}--{glue::glue_collapse(gsub(Sys.Date(), pattern = '-', replacement = ''))}_{set_protein_name}_manual_assignments")
# 
# # save as an rds
# write_rds(x = hit_df, 
#           file = glue::glue("{assignments_folder}/{assignment_df_name}.rds"))
# 
# # save as a csv
# write_csv(x = hit_df, 
#           file = glue::glue("{assignments_folder}/{assignment_df_name}.csv"))
```

Save the by-hit dye figures
```{r}
# ##--- plots the same data as the original plot, but broken into sub-plots by assignment
# full_stacked_screen_p <- 
#    # notice this is the same function used to save the original screen
#   save_dye_screen_figs(tidied_screen, 
#                        plot_type = "divided", # this argument determines which plot is output
#                        hits = hit_df, # only "full_screen" does not require this argument 
#                        # passed to saved_stacked_screen() via ...
#                        .save_path = "plots")
# # sometimes prints this warning, which is nbd. Something about the sub-plot alignment probably need a minor fix but the output plot is fine.
# # `Graphs cannot be vertically aligned unless the axis parameter is set. Placing graphs unaligned.`
# 
# ##--- plots the hits and sensitives, this time, faceting by channel.
# full_stacked_screen_p <- 
#    # notice this is the same function used to save the original screen
#   save_dye_screen_figs(tidied_screen, 
#                        plot_type = "hits_by_channel", # this argument determines which plot is output
#                        hits = hit_df, # only "full_screen" does not require this argument 
#                        # passed to saved_stacked_screen() via ...
#                        .save_path = "plots",
#                        
#                        # increasing `.default_title_height` over it's default (0.5) adds some height to the figure if it's too short, and clipping axes. 
#                        # works like this for all save_dye_screen_figs plots.
#                        .default_title_height = 2 
#                        )
```
